Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2021-06-08 manuscript.tex
Add additional citation, suggested by Reviewer1 [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/504f52655e0083208065c208367146913c6c4b95.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/504f52655e0083208065c208367146913c6c4b95/checks
https://github.com/habi/acinar-analysis-manuscript/runs/918881513

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...46c4c67bf996034873f7ab33969af2db0093951a}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/46c4c67bf996034873f7ab33969af2db0093951a/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/46c4c67bf996034873f7ab33969af2db0093951a}{habi/acinar-analysis-manuscript@46c4c67}
on June 8, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(46c4c67)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(46c4c67)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

The volume and shape of the alveoli, alveolar ducts, and the acini are critical parameters for ventilation and particle deposition {[}\protect\hyperlink{ref-eioib1TQ}{46}--\protect\hyperlink{ref-OT4s1CSX}{48}{]}.
Particle deposition, for example, is relatively low during the first two weeks of a rats' life, high at postnatal day P21 and medium at days P36--P90 {[}\protect\hyperlink{ref-yHHhvOtP}{15},\protect\hyperlink{ref-18DcNLAv6}{16}{]}.
This correlates well with our results, where we found a significantly larger number of alveoli per acinus volume at days 10 and 21 compared to days 4 and 60 (all p-values are smaller than 5.4e-5, which is the p-value found between day 4 and~day 21).
Kreyling et al.~{[}\protect\hyperlink{ref-18DcNLAv6}{16}{]} report maximal gold nanoparticle retention at this time point (see \href{https://pubs.acs.org/doi/10.1021/acsnano.8b01826\#fig1}{their figure 1}).

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} with the DOI \href{https://doi.org/10.1101/786681}{10.1101/786681}.
It has been submited to \href{https://journals.plos.org/plosone/}{\emph{PLOS ONE}}.
The manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/5e778036e316c47b8bac4ce50086b191a7e3707a...504f52655e0083208065c208367146913c6c4b95}{has been updated} since submission.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/504f52655e0083208065c208367146913c6c4b95/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/504f52655e0083208065c208367146913c6c4b95}{habi/acinar-analysis-manuscript@504f526}
on June 8, 2021.

@@

\begin{itemize}
\item
  \textbf{David Haberthür}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3388-9187}{0000-0003-3388-9187}
  · \href{mailto:haberthuer@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(504f526)}{haberthuer@ana.unibe.ch}
  · \includegraphics{images/github.svg}
  \href{https://github.com/habi}{habi}
  · \includegraphics{images/twitter.svg}
  \href{https://twitter.com/habi}{habi}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Eveline Yao}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Sébastien F. Barré}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Tiziana P. Cremona}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-0061-9578}{0000-0003-0061-9578}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Stefan A. Tschanz}
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-3880-4437}{0000-0003-3880-4437}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\item
  \textbf{Johannes C. Schittny}✉
  · \includegraphics{images/orcid.svg}
  \href{https://orcid.org/0000-0003-4025-3961}{0000-0003-4025-3961}
  · \href{mailto:schittny@ana.unibe.ch?subject=Feedback\%20regarding\%20the\%20acinus\%20manuscript\%20(504f526)}{schittny@ana.unibe.ch}
  Institute of Anatomy, University of Bern, Bern, Switzerland
\end{itemize}

@@

The volume and shape of the alveoli, alveolar ducts, and the acini are critical parameters for ventilation and particle deposition {[}\protect\hyperlink{ref-eioib1TQ}{46}--\protect\hyperlink{ref-OT4s1CSX}{48}{]}.
Particle deposition, for example, is relatively low during the first two weeks of a rats' life, high at postnatal day P21 and medium at days P36--P90 {[}\protect\hyperlink{ref-yHHhvOtP}{15},\protect\hyperlink{ref-18DcNLAv6}{16},\protect\hyperlink{ref-VJYqPtdT}{49}{]}.
This correlates well with our results, where we found a significantly larger number of alveoli per acinus volume at days 10 and 21 compared to days 4 and 60 (all p-values are smaller than 5.4e-5, which is the p-value found between day 4 and~day 21).
Kreyling et al.~{[}\protect\hyperlink{ref-18DcNLAv6}{16}{]} report maximal gold nanoparticle retention at this time point (see \href{https://pubs.acs.org/doi/10.1021/acsnano.8b01826\#fig1}{their figure 1}).
